---
title: "Capstone_milestone_Report1"
author: "Rstudio"
date: "August 2, 2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(tidyr)
library(stringr)
library(readr)
library(ggplot2)
```

## R Markdown
Max,

I did further investigations and clean the data most of the part. Below are the certain results I would have attached and mentioned also.

1) Removed Na's from the dataset.
2) Removed unwanted columns and data from the dataset.
3) Now the data set is reduced to 7548 obs. of  13 variables.

```{r}
summary(Youth_Tobacco_Survey_YTS_Data)


```

## Including Plots

Plots inference:
1) I did box plot for character variables which I have attached below. I am not able to distinguish the data inference from the below graphs. Could you please help me which variables would be more helpful in the box plot.

2) I did geom_point with geom_smooth with method as lm, using ggplot. Below are the files I have attached.

What I Inferred is 

a) High confidence limit is increase with the low confidence limit, graph has been attached.
b) I was not able to understand between sample Vs Data_value.
c) I was able to Understand little bit about Data_value Vs Data_value_std_error.

```{r pressure, echo=FALSE}
ggplot(Youth_Tobacco_Survey_YTS_Data, aes(x=Youth_Tobacco_Survey_YTS_Data$Data_Value, y=Youth_Tobacco_Survey_YTS_Data$Data_Value_Std_Err)) + geom_point() + geom_smooth(method = "lm")

ggplot(Youth_Tobacco_Survey_YTS_Data, aes(x=Youth_Tobacco_Survey_YTS_Data$Data_Value, y=Youth_Tobacco_Survey_YTS_Data$Sample_Size)) + geom_point() + geom_smooth(method = "lm")

ggplot(Youth_Tobacco_Survey_YTS_Data, aes(x=Youth_Tobacco_Survey_YTS_Data$High_Confidence_Limit, y=Youth_Tobacco_Survey_YTS_Data$Low_Confidence_Limit)) + geom_point() + geom_smooth(method = "lm")


ggplot(Youth_Tobacco_Survey_YTS_Data, aes(x = Youth_Tobacco_Survey_YTS_Data$MeasureDesc,y = Youth_Tobacco_Survey_YTS_Data$TopicDesc)) + geom_boxplot()

ggplot(Youth_Tobacco_Survey_YTS_Data, aes(x = Youth_Tobacco_Survey_YTS_Data$TopicDesc,y = Youth_Tobacco_Survey_YTS_Data$Response)) + geom_boxplot()

ggplot(Youth_Tobacco_Survey_YTS_Data, aes(x = Youth_Tobacco_Survey_YTS_Data$Gender,y = Youth_Tobacco_Survey_YTS_Data$Education)) + geom_boxplot()
```
